---
title: "Lab 00 - Hello IDS!"
author: "Selena Bobeica"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Kumi Stevens", "Carla Martin", "Ash Warnes", 
           "Shreya", "Brogan"),
  github_username = c("kumi-stevens", "cmartin658", "ashbrw7", 
                      "ggshreya", "Brogan07125"), 
  colour = c("goldenrod1", "green3", "purple", 
             "blue", "pink"),
  hobby = c("clarinet", "football", "art", 
            "cello", "singing"),
  favourite_number = c(3, 9, 7, 2, 5)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```

This is a bar chart that shows what everyone's favourite number is (y-axis). The bars are filled with the favourite colour of that specific person. Each person is identified by their github username (x-axis).

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Name", 
          y = "Favourite number",
          title = "What is everyone's favourite number?")
```

The labs function allows the user to set a title, and label names for the x and y-axis in the bar plot. 

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

The bar chart visualisation method is not as useful when you have a small data set. When the size of the data set increases, you are able to deduce which hobby is the most and least popular in the year. You can also use a pie chart to represent this data visually.